\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex

% Metrics : ROC AUC and AUPRC
In supervised learning terms, the network inference task can be viewed as a
binary classification task where one has to correctly classify the presence
or the absence of edges of the graph. Given the ground true adjacency matrix
$A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
network inference method using the area under the ROC curve (ROC AUC)
and the area under the precision-recall curve (AUPRC)
(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
($(i, i) \not \in E, \forall i \in V$) and some inference methods could
give maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
correlation, we set those elements to the minimum of $\hat{A}$ prior
assessment.

@@

\begin{table}[H]
\centering
\caption{Comparison (ROC) with other methods (for now, $t = 0.11$)}
\begin{tabular}{*{5}{l}}
\toprule
Methods             & normal-1 & normal-2 & normal-3 & normal-4 \\
\midrule
Correlation (best)         & 0.886 & 0.884 & 0.891 & 0.877\\
Partial correlation (best) & 0.932 & 0.931 & 0.930 & 0.928 \\
Our approach               & 0.943 & 0.942 & 0.942 & 0.939 \\
GENIE3                     & & & & \\
GTE                        & 0.890 & 0.893 & 0.894 & 0.873 \\
Directivity                & 0.535 & 0.526 & 0.533 & 0.535 \\
Our approach + dir         & 0.944 & 0.943 & 0.942 & 0.940\\
\bottomrule
\end{tabular}
\end{table}

>>>>

% Metrics : ROC AUC and AUPRC
In supervised learning terms, the network inference task can be viewed as a
binary classification task where one has to correctly classify the presence
or the absence of edges of the graph. Given the ground true adjacency matrix
$A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
network inference method using the area under the ROC curve (AUROC)
and the area under the precision-recall curve (AUPRC)
(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
($(i, i) \not \in E, \forall i \in V$) and some inference methods could
give maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
correlation, we set those elements to the minimum of $\hat{A}$ prior
assessment.

@@

\begin{table}[tbh]
\centering
\caption{TODO}
\begin{tabular}{@{}l *{8}{c}@{}}
\toprule
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\cmidrule(r){2-5}\cmidrule(r){6-9}
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
\midrule
GENIE3                 & & & & & & & & \\
Directivity            & 0.535 & 0.526 & 0.533 & 0.535 & 0.012 & 0.012 & 0.012 & 0.012 \\
Correlation            & 0.886 & 0.884 & 0.891 & 0.877 & 0.153 & 0.145 & 0.170 & 0.132 \\
GTE                    & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142 \\
Partial correlation    & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344 \\
Our approach           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388 \\
Our approach + dir     & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[tbh]
\centering
\caption{TODO}
\begin{tabular}{@{}l *{8}{c}@{}}
\toprule
  & \multicolumn{4}{c}{AUROC} & \multicolumn{4}{c}{AUPRC} \\
\cmidrule(r){2-5}\cmidrule(r){6-9}
Methods $\backslash$ normal- & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 \\
\midrule
No  filtering       & 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
P                   & 0.925 & 0.925 & 0.924 & 0.923 & 0.322 & 0.324 & 0.323 & 0.312\\
P + W               & 0.931 & 0.930 & 0.928 & 0.927 & 0.333 & 0.334 & 0.327 & 0.313\\
P + W + PCA         & 0.932 & 0.931 & 0.930 & 0.928 & 0.364 & 0.366 & 0.359 & 0.344\\
Averaging           & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
Averaging + Directivity & 0.944 & 0.943 & 0.942 & 0.940 & 0.404 & 0.405 & 0.399 & 0.389\\
\bottomrule
\end{tabular}
\end{table}
